Notes and Problems from My Research\vspace{-1ex}

### 2019-01-08 Reading Notes/reading_notes.tex
Add Course Notes and make updates

\usepackage{xcolor, amsmath, amsfonts, amssymb, graphicx, color, fancyhdr, lipsum, scalerel, stackengine, mathrsfs, tikz-cd, mdframed, enumitem, framed, adjustbox}
\usepackage[framed,thmmarks]{ntheorem}
\usepackage[mathscr]{euscript}

@@

%Theorems, Lemmas, and Corollaries
\theoremstyle{changebreak}
\theoremseparator{}
\theoremsymbol{}
\theoremindent0.5cm
\theoremheaderfont{\bfseries} 
\newtheorem{thm}{Theorem}[subsection]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}

@@

%Shade definitions
\theoremindent0cm
\theoremheaderfont{\normalfont\bfseries} 
\def\theoremframecommand{\colorbox[rgb]{.9,.9,1}}
\newshadedtheorem{defn}[thm]{Definition}

@@

%proofs
\theoremstyle{nonumberbreak}
\theoremindent0.5cm
\theoremheaderfont{\sc}
\theoremseparator{}
\theoremsymbol{\ensuremath\spadesuit}
\newtheorem{prf}{Proof}

@@

%schemes
\DeclareMathOperator{\Ga}{\ensuremath\mathbf{G_a}}
\DeclareMathOperator{\Gm}{\ensuremath\mathbf{G_m}}
\newcommand*{\GL}[1]{\ensuremath\mathbf{GL_#1}}
\newcommand*{\SL}[1]{\ensuremath\mathbf{SL_#1}}
\newcommand*{\mun}[1]{\ensuremath\mathbf{\mu_#1}}
\newcommand*{\alp}[1]{\ensuremath\mathbf{\alpha_#1}}

@@

\part{Winter 2019}
This is my first official quarter as Julia's student! My plan for now is to continue working on Waterhouse as well
as learn about algebraic geometry (alongside my usual classes, of course).
\section{Preparation, Waterhouse, and G\"ortz \& Weddhorn}
To give a sense of direction, Julia recommended that I take a look at the following regularity theorem:
\begin{thm}[Smoothness Theorem]\label{smooth}
	Let $G$ be an algebraic affine group scheme over a field $k$. Then $k[G]\otimes \bar k$ is reduced if and
	only if $\dim G = \rank \Omega_{k[G]}$.
\end{thm}
I have quite a bit of information to process before this, so I will get started!
\begin{defn}[Closed Embedding]
	If $G$ and $H$ are affine group schemes represented by $A$ and $B$, respectively and
	if $\psi:H\to G$ is a homomorphism of affine group schemes (locally a group homomorphism)
	then if the corresponding algebra map $A\to B$ is surjective, then $\psi$ is called
	a \textbf{closed embedding.}
\end{defn}

@@

>>>>

\usepackage{amsmath, amsfonts, amssymb, graphicx, color, fancyhdr, lipsum, scalerel, stackengine, mathrsfs, tikz-cd, mdframed, enumitem, framed, adjustbox, bm, upgreek, x	color}
\usepackage[framed,thmmarks]{ntheorem}
\usepackage[mathscr]{euscript}

@@

%Theorems, Lemmas, and Corollaries
\theoremstyle{changebreak}
\theoremseparator{}
\theoremsymbol{}
\theoremindent0.5cm
\theoremheaderfont{\color{blue}\bfseries}

\newtheorem{thm}{Theorem}[subsection]
\theoremheaderfont{\bfseries}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}

@@

%Shade definitions
\theoremindent0cm
\theoremheaderfont{\normalfont\bfseries} 
\def\theoremframecommand{\colorbox[rgb]{.7,.9,1}}
\newshadedtheorem{defn}[thm]{Definition}

@@

%proofs
\theoremstyle{nonumberplain}
\theoremindent0.5cm
\theoremheaderfont{\sc}
\theoremseparator{:}
\theoremsymbol{\ensuremath\spadesuit}
\newtheorem{prf}{Proof}

@@

%schemes
\DeclareMathOperator{\Ga}{\ensuremath\mathbf{G_a}}
\DeclareMathOperator{\Gm}{\ensuremath\mathbf{G_m}}
\newcommand*{\GL}[1]{\ensuremath\mathbf{GL_#1}}
\newcommand*{\SL}[1]{\ensuremath\mathbf{SL_#1}}
\newcommand*{\mun}[1]{\ensuremath\mathbf{\bm\upmu_#1}}
\newcommand*{\alp}[1]{\ensuremath\mathbf{\bm\upalpha_#1}}

@@

\part{Winter 2019}
This is my first official quarter as Julia's student! My plan for now is to continue working on Waterhouse as well
as learn about algebraic geometry (alongside my usual classes, of course).
\section{Affine Group Schemes (Waterhouse)	}
To give a sense of direction, Julia recommended that I take a look at the following regularity theorem:
\begin{thm}[Smoothness Theorem]\label{smooth}
	Let $G$ be an algebraic affine group scheme over a field $k$. Then $k[G]\otimes \bar k$ is reduced if and
	only if $\dim G = \rank \Omega_{k[G]}$.
\end{thm}
I have quite a bit of information to process before this, so I will get started!
\begin{defn}[Closed Embedding]
	If $G$ and $H$ are affine group schemes represented by $A$ and $B$, respectively and
	if $\psi:H\to G$ is a homomorphism of affine group schemes (locally a group homomorphism)
	then if the corresponding algebra map $A\to B$ is surjective, then $\psi$ is called
	a \textbf{closed embedding.}
\end{defn}

@@

\begin{defn}
	A group scheme $G$ represented by $A$ that consists entirely of group-like elements is
	called \textbf{diagonalizable.}
\end{defn}
\begin{rmk}\label{rmk-diag}
	Notice that an alternative definition is to begin with an abelian group $M$ and to 
	define $S,\Delta,$ and $\varepsilon$ such that each element is group-like. The resulting
	Hopf algebra represents a diagonalizable group scheme.
\end{rmk}

Consider the group algebra $k[M]$ on the group in Remark \ref{rmk-diag}. If this algebra
is finitely generated, we get the following:
\begin{thm}
	Let $G$ be diagonalizable and represented by $A$ and assume $A$ is finitely generated
	as a $k$-algebra. Then $G$ is a finite product of copies of $\Gm$ and $\mun n$.
\end{thm}
\begin{prf}
	Let $x_1,\dots, x_n$ be generators for $k[M]=A$. Each $x_i$ can be written as a (finite!)
	$k$-linear combination of elements in $M$, so we can instead use the finitely many $m_i$
	which generate these generators, and this gives us a $k$-algebra basis for $k[M]$. Call this
	new generating set $U$.

	Let $M'$ be the abelian group generated by $U$ and notice that $k[M']$ is a subalgebra of
	$k[M]$ containing $U$ so $k[M']=k[M]$ and therefore $M'=M$. This establishes that $M$ is 
	a finitely generated abelian group, so we can split up the algebra into a tensor product
	of $k[\Z]$ and $k[\Z/n\Z]$.

	When $M=\Z$, 
\end{prf}

\section{Algebraic Geometry}
